Supplementary Information for:

### 2017-03-22 JTB_supp/JTB_supp.Rmd
add yC description

>>>>

#### $y_{C}$: Yield of biomass formation from photosynthate {-}
This coefficient specifies the efficiency of conversion of photosynthate into biomass at the biomass synthesizing units, which combine photosynthate (CH~2~O), ammonia (NH~3~) and O~2~ to form biomass, water, and CO~2~. In order to balance this macrochemical equation, there must be a carbon loss, which is accounted for using $y_{C}$ < 1. We take a value of 0.8 following @Muller:2009io.
```{r yC, echo=F}
0.8
```
C-mol mol C^-1^

Following this macrochemical equation, the amount of CO~2~ produced during biomass formation can be specified as $(1-y_C)j_P/y_C$, where j_P is the production flux of the SU (see equations 13 and 14 in the main text).
<br><br>
